---
title: "Alcohol vs Seat choice"
author: "Cyann Arevalo"
date: "September 17, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$: There is no difference among mean amounts of alcohol consumed per week by row.  
$H_A$: There is a difference among mean amounts of alcohol consumed per week by row.

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summaries
```{r}
favstats(alcohol~Seat,data=davisdata)
```


## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```

## Conclusions
Looking at the tukey model, we can see that although there is no difference between the middle and front seats, there does appear to be a difference between the back seats and both the middle and front seats.

Since the P value is 0.000116 < 0.05, we reject the null hypothesis and conclude that there is a difference between the amount of alcohol consumed and the seat/row that is chosen.  

